\begin{thebibliography}{99}

\bibitem{janssen2023survey} Janssen T., Koppert A., Berkvens R., et al. ``A survey on IoT positioning leveraging LPWAN, GNSS, and LEO-PNT,'' \textit{IEEE Internet Things J.}, vol. 10, no. 13, pp. 11135--11159, Jul. 2023.

\bibitem{grenier2023survey} Grenier A., Lohan E. S., Ometov A., et al. ``A survey on low-power GNSS,'' \textit{IEEE Commun. Surveys Tuts.}, vol. 25, no. 3, pp. 1482--1509, 3rd Quart., 2023.

\bibitem{mao2024intelligent} Mao B., Zhou X., Liu J., et al. ``On an intelligent hierarchical routing strategy for ultra-dense free space optical low earth orbit satellite networks,'' \textit{IEEE J. Sel. Areas Commun.}, vol. 42, no. 5, pp. 1219--1230, May 2024.

\bibitem{zhu2024irs} Zhu Y., Mao B., Kato N. ``IRS-aided high-accuracy positioning for autonomous driving toward 6G: A tutorial,'' \textit{IEEE Veh. Technol. Mag.}, vol. 19, no. 1, pp. 85--92, Mar. 2024.

\bibitem{su2022nlos} Su H., Wu B., Mao X. ``Non-line-of-sight multipath detection method for BDS/GPS fusion system based on deep learning,'' \textit{J. Shanghai Jiaotong Univ. Sci.}, vol. 27, no. 6, pp. 844--854, 2022.

\bibitem{ahmad2019sparse} Ahmad S., Scheinkman L. ``How can we be so dense? The benefits of using highly sparse representations,'' \textit{arXiv preprint arXiv:1903.11257}, 2019.

\bibitem{li2024dictionary} Li Z., Tang J., Zhao H., et al. ``Dictionary learning-structured reinforcement learning with adaptive-sparsity regularizer,'' \textit{IEEE Trans. Aerosp. Electron. Syst.}, vol. 60, no. 2, pp. 1753--1769, Apr. 2024.

\bibitem{zeng2024spatiotemporal} Zeng K., et al. ``A spatiotemporal information-driven cross-attention model with sparse representation for GNSS NLOS signal classification,'' \textit{IEEE Internet Things J.}, vol. 11, no. 19, pp. 31892--31908, 2024.

\bibitem{mohanty2024survey} Mohanty A., Gao G. ``A survey of machine learning techniques for improving Global Navigation Satellite Systems,'' \textit{EURASIP J. Adv. Signal Process.}, p. 73, 2024.

\bibitem{beaucamp2025comparison} Beaucamp B., Leduc L., Servi\`eres M., et al. ``Comparison of GNSS LOS/NLOS labeling techniques based on a 3D model and sky view imagery for soft mobility and vehicle data in urban areas,'' in \textit{Proc. 2025 IEEE/ION Position, Location and Navigation Symposium (PLANS)}, 2025, pp. 1192--1203.

\bibitem{zeng2026environment} Zeng K., Li Z., Xie S., et al. ``Environment-aware GNSS NLOS detection via unsupervised contrastive representation learning,'' \textit{GPS Solutions}, 2026, doi: 10.1007/s10291-026-02044-6.

\bibitem{zhai2025enhancing} Zhai W., Cui Y., Wang L., et al. ``Enhancing GNSS positioning in urban environments: A Transformer-based NLOS detection and adaptive weighting approach,'' \textit{IEEE Internet Things J.}, vol. 12, pp. 43521--43539, 2025.

\bibitem{qi2025modelling} Qi X., Xu B. ``Modelling and assessing reinforcement learning-assisted GNSS multipath estimation and mitigation for urban navigation,'' \textit{IEEE Trans. Veh. Technol.}, 2025, doi: 10.1109/TVT.2025.3625730.

\bibitem{xu2025conv\_lstm} Xu Z., Petrunin I., Tsourdos A., et al. ``NLOS signal detection from early--late prompt correlators using convolutional LSTM network,'' \textit{Eng. Proc.}, vol. 88, no. 1, p. 77, 2025.

\bibitem{qin2025bds} Qin Y., Li Z., Xie S., et al. ``Non-line-of-sight multipath classification method for BDS using convolutional sparse autoencoder with LSTM,'' \textit{Tsinghua Sci. Technol.}, vol. 30, pp. 68--86, 2025.

\bibitem{survey\_brain2024} ``The new generation brain-inspired sparse learning: A comprehensive survey,'' 2024.

\bibitem{xu2024cross\_modal} Xu Y., Hu C., Lee G. H. ``Rethink cross-modal fusion in weakly-supervised audio-visual video parsing,'' in \textit{Proc. WACV}, 2024, pp. 5615--5624.

\bibitem{li2023nlos} Li Z., Zeng K., Wang L., et al. ``NLOS/LOS classification by constructing indirect environment interaction from GNSS receiver measurements using a Transformer-based deep learning model,'' in \textit{Proc. ION GNSS+}, 2023, pp. 859--870.

\bibitem{zheng2025stacking} ``Detection of GNSS NLOS signals in urban environments via stacking ensemble learning and signal features,'' \textit{Measurement}, 2025, doi: 10.1016/j.measurement.2025.115265.

\bibitem{titouni2025cnn} Titouni S., Messaoudene I., Himeur Y., et al. ``Enhancing GNSS localization in urban canyons with a hybrid CNN-Autoencoder approach to LOS/NLOS classification,'' \textit{IEEE Access}, vol. 13, pp. 164426--164441, 2025.

\bibitem{applied\_soft2025} ``Intelligent urban GNSS measurement uncertainty prediction by exploring the spatial characteristics with transformer,'' \textit{Applied Soft Computing}, 2025.

\bibitem{zhu2025carnet} Zhu N., He R., Wang Z., et al. ``CarNet: A generative convolutional neural network-based line-of-sight/non-line-of-sight classifier for global navigation satellite systems by transforming multivariate time-series data into images,'' \textit{Eng. Appl. Artif. Intell.}, 2025, doi: 10.1016/j.engappai.2025.110450.

\bibitem{xu2024ml_gnss} Xu P., Zhang G., Yang B., et al. ``Machine Learning in GNSS Multipath/NLOS Mitigation: Review and Benchmark,'' \textit{IEEE Aerosp. Electron. Syst. Mag.}, vol. 39, no. 9, pp. 26--44, Sep. 2024, doi: 10.1109/MAES.2024.3395182.

\bibitem{dual_self_attention2025} ``Mitigating NLOS Interference in GNSS Single-Point Positioning Based on Dual Self-Attention Networks,'' \textit{IEEE Internet Things J.}, vol. 12, no. 4, pp. 4318--4330, 2025.

\bibitem{attention_gans2025} ``Attention-GANs: An Advanced GNSS Data Augmentation Method for Improved NLOS/LOS Classification,'' in \textit{ISPRS Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}, 2025.

\bibitem{li2024gnss_positioning} Li F., Zhai C., Xie T., et al. ``GNSS positioning enhancement based on NLOS signal detection using spatio-temporal learning in urban canyons,'' \textit{GPS Solutions}, vol. 28, no. 4, p. 209, 2024.

\bibitem{li2026graph} Li Z., Cao M., Zeng K., et al. ``A graph contrastive learning-based semi-supervised GNSS NLOS signal recognition method,'' \textit{GPS Solutions}, vol. 30, no. 1, p. 42, 2026.

\bibitem{zhang2021lstm} Zhang G., Xu P., Xu H., et al. ``Prediction on the urban GNSS measurement uncertainty based on deep learning networks with long short-term memory,'' \textit{IEEE Sensors J.}, vol. 21, no. 18, pp. 20563--20577, 2021.

\bibitem{jiang2025outlier} Jiang Y., Zhou Z., Zhang Y., et al. ``Deep-learning enhanced outlier detection for precise GNSS positioning with smartphones,'' \textit{IEEE Trans. Instrum. Meas.}, vol. 74, pp. 1--13, 2025.

\bibitem{zhao2025ensemble} 赵一鑫, 韩昆, 许睿涛, 等. ``集成学习辅助的GNSS异常信号探测与定位,'' \textit{大地测量学与导航}, vol. 50, no. 9, pp. 1--10, 2025.

\end{thebibliography}
